P.berghei pir analysis

### 2021-05-13 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Saving png files as PDFs
Fixing figure 2A bar chart order of stacks

@@

y <- ggplot(data = tpm_data_SorL_stackgenes, 
            aes(
              x = stage_num,
              y = total_tpm, 
              fill = SorL,
              group = stage_num
            )) +
  geom_rect(
    aes(
      xmin = stage_num - .7,
      xmax = stage_num + .7,
      ymin = -Inf,
      ymax = Inf,
      fill = stage_col
    ),
    alpha = .05
  ) +
  geom_bar(position = position_stack(),
           stat = 'identity',
           colour = 'black',
           size = 0.1) +
  scale_fill_manual(
    breaks = unique(tpm_data_SorL_stackgenes$SorL),
    values = c(
      SorL_col_num,
      fills
    )
  )+
  scale_color_manual('black') + 
  labs(fill = stack_label) +
  scale_y_continuous(breaks = max_tpm) +
  theme_classic() +
  # scale_size(range = c(0,3)) +
  ylab(
    bquote('total '~italic(.('pir'))~' TPM')
  ) +
  scale_x_continuous(
    breaks = tpm_data_SorL_stackgenes$stage_num %>% unique(),
    labels = tpm_data_SorL_stackgenes$stage %>% unique(),
    expand = c(0, 0)
  ) +
    theme(
      axis.text.x = element_text(angle = 90, 
                                 vjust = .5,
                                 size = 10),
      axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.key.size = unit(3,'mm'),
    legend.key.width = unit(2,'mm'),
    ) +
    xlab('stage') + 
    facet_grid(.~stage, 
               scales = "free_x",
               space = "free_x") +
    scale_x_discrete(expand=c(0,0)) +
    theme(
      axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x = element_blank(),
      # axis.line.x = element_blank(),
      axis.text.y = element_text(size = 10),
      axis.title.y = element_text(size = 10),
      legend.title = element_text(size = 12),
      legend.text = element_text(size = 10),
      legend.key.size = unit(3,'mm'),
      legend.key.width = unit(2,'mm'),
      strip.text.x = element_text(size=8, 
                                  face = 'bold', 
                                  angle = 90),
      strip.background = element_rect(
        color="black", 
        size=0.1, 
        linetype="solid"
      ),
      panel.spacing.x = unit(0, "null")
    )

@@

y <- ggplot(data = tpm_data_SorL_stackgenes_low, 
            aes(
              x = stage,
              y = total_tpm, 
              fill = SorL,
              group = stack_group_order
            )) +
  geom_bar(position = position_stack(),
           stat = 'identity',
           colour = 'black',
           size = 0.1) +
  scale_fill_manual(
    breaks = unique(tpm_data_SorL_stackgenes_low$SorL),
    values = SorL_col_num
  ) +
  scale_color_manual('black') + 
  labs(fill = stack_label) +
  scale_y_continuous(breaks = max_tpm) +
  theme_classic() +
  scale_size(range = c(0,3)) +
  ylab(
    bquote('total '~italic(.('pir'))~' TPM')
  ) + 
  facet_grid(.~stage, 
             scales = "free_x",
             space = "free_x") +
  scale_x_discrete(expand=expand_scale(add=1)) +
  theme(
    axis.title.x=element_blank(),
    axis.text.x=element_blank(),
    axis.ticks.x = element_blank(),
    # axis.line.x = element_blank(),
    axis.text.y = element_text(size = 15),
    axis.title.y = element_text(size = 8),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 5),
    legend.key.size = unit(3,'mm'),
    legend.key.width = unit(2,'mm'),
    strip.text.x = element_text(size=6, 
                                face = 'bold', 
                                angle = 90),
    strip.background = element_rect(
      color="black", 
      size=0.1, 
      linetype="solid"
    ),
    panel.spacing.x = unit(0, "null")
  )

>>>>

pdf(file = 'Manuscript_suppfig1A_corrplot_all_experiments_rnaseq.pdf',
    height = 5,
    width = 5)
corrplot(cor(big_top_recast), method = 'color', 
         order = 'hclust', hclust.method = 'ward.D2',
         cl.lim = c(-0.036,1), tl.cex = 0.50,
         col = c(viridis(100), magma(115)), addrect = 6)
dev.off()

@@

y <- ggplot(data = tpm_data_SorL_stackgenes, 
            aes(
              x = stage_num,
              y = total_tpm, 
              fill = SorL,
              # group = stage_num
            )) +
  geom_rect(
    aes(
      xmin = stage_num - .7,
      xmax = stage_num + .7,
      ymin = -Inf,
      ymax = Inf,
      fill = stage_col
    ),
    alpha = .05
  ) +
  geom_bar(position = position_stack(),
           stat = 'identity',
           colour = 'black',
           size = 0.1) + 
  scale_fill_manual(
    breaks = unique(tpm_data_SorL_stackgenes$SorL),
    values = c(
      SorL_col_num,
      fills
    )
  ) +
  scale_color_manual('black') + 
  # labs(fill = stack_label) +
  scale_y_continuous(breaks = max_tpm) +
  theme_classic() +
  # scale_size(range = c(0,3)) +
  ylab(
    bquote('total '~italic(.('pir'))~' TPM')
  ) +
  scale_x_continuous(
    breaks = tpm_data_SorL_stackgenes$stage_num %>% unique(),
    labels = tpm_data_SorL_stackgenes$stage %>% unique(),
    expand = c(0, 0)
  ) +
    theme(
      axis.text.x = element_text(angle = 90, 
                                 vjust = .5,
                                 size = 10),
      axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 10),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.key.size = unit(3,'mm'),
    legend.key.width = unit(2,'mm'),
    ) +
    xlab('stage') + 
    facet_grid(.~stage, 
               scales = "free_x",
               space = "free_x") +
    scale_x_discrete(expand=c(0,0)) +
    theme(
      axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x = element_blank(),
      # axis.line.x = element_blank(),
      axis.text.y = element_text(size = 10),
      axis.title.y = element_text(size = 10),
      legend.title = element_text(size = 12),
      legend.text = element_text(size = 10),
      legend.key.size = unit(3,'mm'),
      legend.key.width = unit(2,'mm'),
      strip.text.x = element_text(size=8, 
                                  face = 'bold', 
                                  angle = 90),
      strip.background = element_rect(
        color="black", 
        size=0.1, 
        linetype="solid"
      ),
      panel.spacing.x = unit(0, "null")
    )

@@

y <- ggplot(data = tpm_data_SorL_stackgenes_low, 
            aes(
              x = stage,
              y = total_tpm, 
              fill = SorL,
              # group = stage_num
            )) +
  geom_bar(position = position_stack(),
           stat = 'identity',
           colour = 'black',
           size = 0.1) + 
  scale_fill_manual(
    breaks = unique(tpm_data_SorL_stackgenes$SorL),
    values = c(
      SorL_col_num,
      fills
    )
  ) +
  scale_color_manual('black') + 
  labs(fill = stack_label) +
  scale_y_continuous(breaks = max_tpm) +
  theme_classic() +
  scale_size(range = c(0,3)) +
  ylab(
    bquote('total '~italic(.('pir'))~' TPM')
  ) + 
  facet_grid(.~stage, 
             scales = "free_x",
             space = "free_x") +
  scale_x_discrete(expand=expand_scale(add=1)) +
  theme(
    axis.title.x=element_blank(),
    axis.text.x=element_blank(),
    axis.ticks.x = element_blank(),
    # axis.line.x = element_blank(),
    axis.text.y = element_text(size = 15),
    axis.title.y = element_text(size = 8),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 5),
    legend.key.size = unit(3,'mm'),
    legend.key.width = unit(2,'mm'),
    strip.text.x = element_text(size=6, 
                                face = 'bold', 
                                angle = 90),
    strip.background = element_rect(
      color="black", 
      size=0.1, 
      linetype="solid"
    ),
    panel.spacing.x = unit(0, "null")
  )
